Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-04-27 博士/论文提交/adversarial_attack/TCSVT/latex/imperceptible.tex
更新作者信息

% 题目
\hyphenation{op-tical net-works semi-conduc-tor}
\begin{document}
\title{Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking}
\author{
  Zhenbang Li, Jin Gao, Yaya Shi, Shaoru Wang, Bing Li, Weiming Hu
  \thanks{This work is supported by the national key R\&D program of china (No. 2018AAA0102802, No. 2018AAA0102803, No. 2018AAA0102800), the Natural Science Foundation of China (Grant No. 62036011, 61721004, 61772225), the Key Research Program of Frontier Sciences, CAS, Grant No. QYZDJ-SSW-JSC040, and the National Natural Science Foundation of Guangdong (No. 2018B030311046). \textit{(Corresponding author: Jin Gao.)}}

  \thanks{Z. Li, J. Gao, Shaoru Wang and B. Li are with the National Laboratory of Pattern Recognition, Institute of Automation, Chinese Academy of Sciences, Beijing, 100190, China, and also with School of Artificial Intelligence, University of Chinese Academy of Sciences, Beijing, 100190, China (e-mail: zhenbang.li@nlpr.ia.ac.cn; jin.gao@nlpr.ia.ac.cn; shaoru.wang@nlpr.ia.ac.cn; bli@nlpr.ia.ac.cn).}
  \thanks{Y. Shi is with the University of Science and Technology of China, Anhui, 230026, China (e-mail: shiyaya@mail.ustc.edu.cn).}
  \thanks{W. Hu is with CAS Center for Excellence in Brain Science and Intelligence Technology, National Laboratory of Pattern Recognition, Institute of Automation, Chinese Academy of Sciences, Beijing, 100190, China, and also with School of Artificial Intelligence, University of Chinese Academy of Sciences, Beijing, 100190, China (e-mail: wmhu@nlpr.ia.ac.cn).}
}

@@

% 作者
%\vfill  % 距离更远了
%\enlargethispage{-5in}  % 距离近了些
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/zhbli.jpg}}]
\begin{IEEEbiographynophoto}
{Zhenbang Li}
received the B.S. degree in computer science and technology from Beijing Institute of Technology, Beijing, China, in 2016. Currently, he is a Ph.D. student with the Institute of Automation, Chinese Academy of Sciences, Beijing, China. His research interests include object tracking and deep learning.
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}
{Jin Gao}
received the B.S. degree from the Beihang University, Beijing, China in 2010, and the Ph.D. degree from the University of Chinese Academy of Sciences (UCAS) in 2015. Now he is an assistant professor with the National Laboratory of Pattern Recognition, Institute of Automation, Chinese Academy of Sciences (CASIA). His research interests include visual tracking, autonomous vehicles, and service robots. 
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}
{YaYa Shi}
received the B.S. degree from the Hefei University of Technology, Anhui, China in 2018. Currently, She is a Ph.D. student with the University of Science and Technology of China, Anhui, China. Her research interests include video captioning and deep learning.
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}
{Bing Li}
received the Ph.D. degree from the Department of Computer Science and Engineering, Beijing Jiaotong University, China, in 2009. He is currently a Professor with the Institute of Automation, Chinese Academy of Sciences, Beijing, China. His research interests include video understanding, color constancy, visual saliency, and web content mining.
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}
{Weiming Hu}
received the Ph.D. degree from the Department of Computer Science and Engineering, Zhejiang University, in 1998. From April 1998 to March 2000, he was a postdoctoral research fellow with the Institute of Computer Science and Technology, Peking University. Now he is a professor with the Institute of Automation, Chinese Academy of Sciences. His research interests include visual surveillance and filtering of Internet objectionable information.
\end{IEEEbiographynophoto}

>>>>

% 题目
\hyphenation{op-tical net-works semi-conduc-tor}
\begin{document}
\title{Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking}
\author{
  Zhenbang Li, Jin Gao, Yaya Shi, Shaoru Wang, Bing Li, Pengpeng Liang, Weiming Hu
  \thanks{This work is supported by the national key R\&D program of china (No. 2018AAA0102802, No. 2018AAA0102803, No. 2018AAA0102800), the Natural Science Foundation of China (Grant No. 62036011, 61721004, 61772225), the Key Research Program of Frontier Sciences, CAS, Grant No. QYZDJ-SSW-JSC040, and the National Natural Science Foundation of Guangdong (No. 2018B030311046). \textit{(Corresponding author: Jin Gao.)}}

  \thanks{Z. Li, J. Gao, Shaoru Wang and B. Li are with the National Laboratory of Pattern Recognition, Institute of Automation, Chinese Academy of Sciences, Beijing, 100190, China, and also with School of Artificial Intelligence, University of Chinese Academy of Sciences, Beijing, 100190, China (e-mail: zhenbang.li@nlpr.ia.ac.cn; jin.gao@nlpr.ia.ac.cn; shaoru.wang@nlpr.ia.ac.cn; bli@nlpr.ia.ac.cn).}
  \thanks{Y. Shi is with the University of Science and Technology of China, Anhui, 230026, China (e-mail: shiyaya@mail.ustc.edu.cn).}
  \thanks{P. Liang is with Zhengzhou University, Henan, 450001, China (e-mail: liangpcs@gmail.com).}
  \thanks{W. Hu is with CAS Center for Excellence in Brain Science and Intelligence Technology, National Laboratory of Pattern Recognition, Institute of Automation, Chinese Academy of Sciences, Beijing, 100190, China, and also with School of Artificial Intelligence, University of Chinese Academy of Sciences, Beijing, 100190, China (e-mail: wmhu@nlpr.ia.ac.cn).}
}

@@

% 作者
%\vfill  % 距离更远了
%\enlargethispage{-5in}  % 距离近了些
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/zhbli.jpg}}]
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images_imperceptible/author/zhbli.jpg}}]
{Zhenbang Li}
received the B.S. degree in computer science and technology from Beijing Institute of Technology, Beijing, China, in 2016. Currently, he is a Ph.D. student with the Institute of Automation, Chinese Academy of Sciences, Beijing, China. His research interests include object tracking and deep learning.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images_imperceptible/author/JGao.pdf}}]
{Jin Gao}
received the B.S. degree from the Beihang University, Beijing, China in 2010, and the Ph.D. degree from the University of Chinese Academy of Sciences (UCAS) in 2015. Now he is an assistant professor with the National Laboratory of Pattern Recognition, Institute of Automation, Chinese Academy of Sciences (CASIA). His research interests include visual tracking, autonomous vehicles, and service robots. 
\end{IEEEbiography}

\begin{IEEEbiography}
{YaYa Shi}
received the B.S. degree from the Hefei University of Technology, Anhui, China in 2018. Currently, She is a Ph.D. student with the University of Science and Technology of China, Anhui, China. Her research interests include video captioning and deep learning.
\end{IEEEbiography}

\begin{IEEEbiography}
{Shaoru Wang}
???
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images_imperceptible/author/bli.pdf}}]
{Bing Li}
received the Ph.D. degree from the Department of Computer Science and Engineering, Beijing Jiaotong University, China, in 2009. He is currently a Professor with the Institute of Automation, Chinese Academy of Sciences, Beijing, China. His research interests include video understanding, color constancy, visual saliency, and web content mining.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images_imperceptible/author/Pengpeng-Liang.pdf}}]
{Pengpeng Liang}
...
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images_imperceptible/author/wmhu.pdf}}]
{Weiming Hu}
received the Ph.D. degree from the Department of Computer Science and Engineering, Zhejiang University, in 1998. From April 1998 to March 2000, he was a postdoctoral research fellow with the Institute of Computer Science and Technology, Peking University. Now he is a professor with the Institute of Automation, Chinese Academy of Sciences. His research interests include visual surveillance and filtering of Internet objectionable information.
\end{IEEEbiography}
